PANCHANGE_data_preprocessing

### 2020-07-22 PANCHANGE_data_preprocessing2020-07-15.Rmd
reviewed IBD exclusion chunks - these still need editing as don't have the data

dat.no.sex.no.age.no.ibd <- dat.no.sex.no.age
```

@@

dat.no.sex.no.age.no.ibd.incomplete.questionnaire <- dat.no.sex.no.age.no.ibd
```

Create tidy data on which the exclusionc criteria have been applied
```{r Tidy data}
dat.glad <- dat.no.sex.no.age.no.ibd.incomplete.questionnaire

skimr::skim(dat.glad)
```
The complete rate for age and sex should be 1 now

>>>>

dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age
```

@@

dat.no.sex.no.gender.no.age.no.ibd.incomplete.questionnaire <- dat.no.sex.no.gender.no.age.no.ibd
```

Create tidy data on which the exclusion criteria have been applied
```{r Tidy data}
dat.glad <- dat.no.sex.no.gender.no.age.no.ibd.incomplete.questionnaire

skimr::skim(dat.glad)
```
The complete rate for sex, gender and age should be 1 now.
